Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1204
Dear Prof. Ren and Song,

Jianjie and I were working on the CLT for superprocesses with stable branching.
In this newest version, under the simplest setting ( super OU-process with simple stable branching), we were finally able to walk through every proofs and details. 
Please take a look.

Best,
Zhenyao

%%%----Versions-----------------------------
% supCLT6.tex 2018/11/29 by Zhenyao
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,oneside,english]{amsart}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

	The existence of superprocesses are well known, see \cite{EB} for instance.
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    :=
    e^{\alpha t} T_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
$
	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
$
and
$
	Q f:= Q_{\kappa_f}f.
$
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\begin{comment}

	\deleted{
	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by
	\begin{align}
	     \mathcal{P}_{\kappa}
    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
	\end{align}
	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
	Then
	\begin{itemize}
	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.

	\end{itemize}
	}
\end{comment}
\subsection{}
    Let $X$ be the super OU-process discussed in the first subsection.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

@@

In this subsection, we will give the main results of this paper. In the remainder of this paper,whenever we deal with an initial configuration $\mu \in \mathcal{M}(\mathbb{R}^d)$, we are implicitly assuming that it has a compact support.
\subsubsection{Large Branching Rate}

@@

     Moreover, if $f$ is twice differentiable and its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{rem}
    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0<\gamma<\beta$.

    Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{rem}

\subsubsection{Critical Branching Rate}
For $f\in \mathcal{P}$, define
$$\tilde{m}[f]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
where
$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
Denote by $D$ the extinction event of super process.
\begin{thm}\label{Theorem12}
Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]).$$
\end{thm}

@@

\section{Preliminaries}
    In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
$
   	\mathcal I_a^b Y
    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
$
	Then we have an nature incremental decomposition of $Y$:
\begin{align}
    \mathcal I_0^t Y
    = \sum_{k = 0}^{\lfloor t \rfloor - 1} \mathcal I_k^{k+1}Y + \mathcal I_{\lfloor t \rfloor}^t Y,
    \quad t\geq 0.
\end{align}
	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
\begin{comment}

\deleted{	
	In this case we have
\begin{align}
    I_a^b[\langle g,X_t\rangle]
    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
\end{align}
}
\end{comment}
    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
    \begin{comment}

@@

    Proof of (3): According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
\[
    |\Psi_0 f(x)| = |f(x)^{1+\beta}| \leq C_{\ref{lem: Lip of power function}} |f(x)|^{1+\beta}.
\]
    Also note that $f\mapsto |f|^{1+\beta}$ is monotonic and $(1+\beta)$-scalable.

@@

    Proof of (5): Notice that from Lemma \ref{lem: Lip of power function},
\[
    |\Psi_0(-U_t f) - \Psi_0(-iT_t^\alpha f) |
    \leq  C_{\ref{lem: Lip of power function}} |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
\]
    From (1), (2), (4) and Lemma \ref{lem: property of controllable operators} (3,4) we get the desired result.

@@

\begin{lem}\label{lem: control of mgtrs}
	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
\[
    \sup_{g \in \mathcal P: Q_\kappa g\leq h} \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
\]
\end{lem}

@@

Denote

>>>>

%%%----Versions-----------------------------
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

	The existence of superprocesses are well known, see \cite{EB} for instance.
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define 
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    :=
    e^{\alpha t} T_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
$
	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
$
and
$
	Q f:= Q_{\kappa_f}f.
$
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\begin{comment}

	\deleted{
	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by
	\begin{align}
	     \mathcal{P}_{\kappa}
    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
	\end{align}
	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
	Then
	\begin{itemize}
	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.

	\end{itemize}
	}
\end{comment}
\subsection{}
    Let $X$ be the super OU-process discussed in the first subsection.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ the value of the L\'evy exponent of infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

@@

In this subsection, we will give the main results of this paper. Let $\mu\in \mathcal M_c(\mathbb R_d)$ be a finite measure on $\mathbb R_d$ with compact support.
\subsubsection{Large Branching Rate}

@@

     Moreover, if $f$ is twice differentiable and its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{rem}
    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0<\gamma<\beta$. Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{rem}

\subsubsection{Critical Branching Rate}
For $f\in \mathcal{P}$, define
$$\tilde{m}[f]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
where
$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
Denote by $D$ the extinction event of the super OU-process.
\begin{thm}\label{Theorem12}
Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\tilde{m}[\theta f]).$$
\end{thm}

@@

\section{Preliminaries}
\begin{comment}

\deleted{	
	In this case we have
\begin{align}
    I_a^b[\langle g,X_t\rangle]
    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
\end{align}
}
\end{comment}

    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that, for each $s\in \Lambda$, $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$.
    \begin{comment}

@@

    Proof of (3): According to Lemma \ref{lem: Lip of power function}, for each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
\[
    |\Psi_0 f(x)| = |f(x)^{1+\beta}| = |f(x)|^{1+\beta}.
\]
    Also note that $f\mapsto |f|^{1+\beta}$ is monotonic and $(1+\beta)$-scalable.

@@

    Proof of (5): Notice that from Lemma \ref{lem: Lip of power function},
\[
    |\Psi_0(-U_t f) - \Psi_0(-iT_t^\alpha f) |
    \leq  (1+\beta) |U_u f-iT_u^{\alpha}f|(|U_u f|^{\beta}+|i T_u^{\alpha}f|^{\beta}).
\]
    From (1), (2), (4) and Lemma \ref{lem: property of controllable operators} (3,4) we get the desired result.

@@

\begin{lem}
\label{lem: control of mgtrs}
	For each $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exist a constant $C > 0$, such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$, we have
\[
    \sup_{g \in \mathcal P: Q_\kappa g\leq h} \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
\]
\end{lem}

@@

\end{prop}
\begin{proof}
	Let $C,\delta > 0$ be the constant in Corollary \ref{cor: used in next corollary}.
